Learning and calibrating per-location classifiers for visual place recognition\thanks{

### 2015-12-03 manuscript.tex
minor eidts

  In this work, we also take advantage of geotags as an available form of supervision and investigate whether the place recognition problem can be cast as a classification task.
  {
    Learning visual classifiers has been investigated for landmark recognition~\cite{Li09} where consumer photographs were clustered into landmark classes based on geo-tags. 
    In this work we wish to recognize individual street locations rather than a small number of landmarks, and as a consequence have only a few (1-5) photographs
    %available for each place.   
    \textcolor{petr}{capturing the same location}.
    In particular, we train a classifier {\em for each location on the map} in a similar manner to per-exemplar classification in object recognition~\cite{Malisiewicz11}. 
    \textcolor{petr}{
      By \em{location} we mean a scene captured by a camera, hence using our terminology, a camera heading to the north captures different location than a camera heading to the south, even those cameras share the same GPS location. 
    }
  }

@@

    Given this choice of $\alpha_j$ and $\beta_j$ 
    \textcolor{petr}{
      the bias term in eq. \eqref{eq:linear2} cancels out and
    }
    the calibrated classification score~\eqref{eq:linear2} reduces to
    %
      \begin{align}
        f_j(\vec{q}) = \dfrac{1}{||\vec{w}_j||}\vec{w}_j^T\vec{q} = \vec{\widetilde{w}}_j^T\vec{q}.
        \label{eq:linear3}
      \end{align}
    %
    % The intuition is that when $\vec{q}$ is $L_2$ normalized, equation~\eqref{eq:linear3} is equivalent to computing the normalized dot-product between vectors $\vec{q}$ and $\vec{w}$. 
    \textcolor{petr}{
      Since $\vec{q}$ is $L_2$ normalized, the reason of particular choice of $\alpha_j$ and $\beta_j$ is that the equation equation~\eqref{eq:linear3} is equivalent to computing the normalized dot-product between vectors $\vec{q}$ and $\vec{w}$.
    }
    This was found to work well in image retrieval~\cite{Sivic03} or matching whitened HOG descriptors~\cite{Doersch13}.
    In this work we investigate whether this intuition about descriptor matching can be used as a form of calibration for the learnt place-specific classifier.

@@

    In table~\ref{tab:recallBOW}, we also compare performance to our implementation of the confuser suppression approach (Conf. supp.) of~\cite{Knopp2010} that, in each database image, detects and removes features that frequently appear at other far-away locations (using parameters $t=3.5$ and $w=70$).  
    % R1:
    %The results show an improvement by our method, specially at recall@1.
    \textcolor{petr} {Our results show an improvements, specially at recall@1.}

@@

      We observe that in $237$ cases a low-ranked true positive image by the baseline (ranked $40-70$)  is attracted into the short list by the w-norm method, resulting in an improvement.  Note that in many other cases our method improves ranking but here we only count the cases for which the baseline method does not have any true positives in the top $20$ short-list. 
      %R1
      % On the other hand, in $39$ cases our method makes the results worse and removes a correct image from the top $20$ short-list but typically only to top $40$.
      \textcolor{petr}{On the other hand, in $39$ cases our method downgrades images from the top $20$ short-list. However, these images typically occur in top 40 shortlist.}

      Finally, we observe that \textcolor{petr} {the downgrading} typically occurs on hard examples where the baseline performance is already bad. 
      %R1
      % When visually inspecting the failure cases we observed that our method typically fails on queries containing a big portion of the sky clouds or vegetation, narrow streets or tunnels and sometimes retrieves images capturing the same building from a different viewpoint or a larger distance.
      \textcolor{petr}{
        When visually inspecting the failure cases we observed that our method typically fails on queries containing a big portion of the sky clouds or vegetation and images containing narrow streets and tunnels. Our method sometimes retrieves images capturing the same building from a different viewpoint or a larger distance.
      }

>>>>

  In this work, we also take advantage of geotags as an available form of supervision and investigate whether the place recognition problem can be cast as a classification task.
  {
    Learning visual classifiers has been investigated for landmark recognition~\cite{Li09} where consumer photographs were clustered into landmark classes based on geo-tags. 
    In this work we wish to recognize individual street locations rather than a small number of landmarks, and as a consequence have only a few (1-5) photographs
    %available for each place.   
    \textcolor{petr}{capturing the same location}.
    In particular, we train a classifier {\em for each location on the map} in a similar manner to per-exemplar classification in object recognition~\cite{Malisiewicz11}. 
    \textcolor{petr}{
      By \em{location} we mean a scene captured by a camera, hence using our terminology, a camera heading to the north captures different location than a camera heading to the south, even though these two cameras share the same GPS location. 
    }
  }

@@

    Given this choice of $\alpha_j$ and $\beta_j$ 
    \textcolor{petr}{
      the bias term in eq. \eqref{eq:linear2} cancels out and
    }
    the calibrated classification score~\eqref{eq:linear2} reduces to
    %
      \begin{align}
        f_j(\vec{q}) = \dfrac{1}{||\vec{w}_j||}\vec{w}_j^T\vec{q} = \vec{\widetilde{w}}_j^T\vec{q}.
        \label{eq:linear3}
      \end{align}
    %
    % The intuition is that when $\vec{q}$ is $L_2$ normalized, equation~\eqref{eq:linear3} is equivalent to computing the normalized dot-product between vectors $\vec{q}$ and $\vec{w}$. 
    \textcolor{petr}{
      Since $\vec{q}$ is $L_2$ normalized, the outcome of the particular choice of $\alpha_j$ and $\beta_j$ is that the equation~\eqref{eq:linear3} is equivalent to computing the normalized dot-product between vectors $\vec{q}$ and $\vec{w}$.
    }
    This was found to work well in image retrieval~\cite{Sivic03} or matching whitened HOG descriptors~\cite{Doersch13}.
    In this work we investigate whether this intuition about descriptor matching can be used as a form of calibration for the learnt place-specific classifier.

@@

    In table~\ref{tab:recallBOW}, we also compare performance to our implementation of the confuser suppression approach (Conf. supp.) of~\cite{Knopp2010} that, in each database image, detects and removes features that frequently appear at other far-away locations (using parameters $t=3.5$ and $w=70$).  
    % R1:
    %The results show an improvement by our method, specially at recall@1.
    \textcolor{petr} {Our results show an improvement, specially at recall@1.}

@@

      We observe that in $237$ cases a low-ranked true positive image by the baseline (ranked $40-70$)  is attracted into the short list by the w-norm method, resulting in an improvement.  Note that in many other cases our method improves ranking but here we only count the cases for which the baseline method does not have any true positives in the top $20$ short-list. 
      %R1
      % On the other hand, in $39$ cases our method makes the results worse and removes a correct image from the top $20$ short-list but typically only to top $40$.
      \textcolor{petr}{On the other hand, in $39$ cases our method downrankes correct images from the top $20$ short-list. However, these images are typically downranked only slightly and still occur in top 40 shortlist.}

      Finally, we observe that \textcolor{petr} {the downranking} typically occurs on hard examples where the baseline performance is already bad. 
      %R1
      % When visually inspecting the failure cases we observed that our method typically fails on queries containing a big portion of the sky clouds or vegetation, narrow streets or tunnels and sometimes retrieves images capturing the same building from a different viewpoint or a larger distance.
      \textcolor{petr}{
        When visually inspecting the failure cases we have observed that our method typically fails on queries containing a large amount of sky with clouds or vegetation and images containing narrow streets and tunnels. Our method also sometimes retrieves images capturing the same building from a different side or a large distance.
      }
